Will Kamala Harris will win the 2024 Presidential election

### 2024-11-04 paper/paper.qmd
References and spelling edits

@@

Arizona is a very important swing state especially as the state has switches which party they voted for in in the last two elections with Trump winning 49% of the vote and Clinton with 45.5%, which considering Arizona is a swing state is a rather significant6 margin. While in the 2020 election Biden ended up winning Arizona with 49.4% of the vote and Trump 49.1%, which is a much smaller margin of victory and what makes Arizona so questionable in the 2024 election. We can see in @fig-supportAM that while the polling numbers for Harris started somewhat low around 42%, the have gone up significantly and have continued to trend upwards in the most recent polls. Although, in the @fig-supportstate trump still has larger support in the state, and the largest polling difference in Trump's favour out of all the swing states polled.

@@

In @fig-supportGNN at the beginning of the polling data the support for Harris was relatively low, while it did start to grow the polling percentage somewhat plateaued at around 47.5% and does not show any signs of growing. Furthermore, in @fig-supportstate we can see that Trump has the edge over Harris considering all of these factors there is a very real possibility that Trump does win Georgia at the end of the day.

@@

Nevada is a state who's majority is dessert and wilderness, with two large cities being Reno and Las Vegas, as the case is with many states a Majority of democratic votes come from large cities and the majority of republican votes coming from rural areas. Nevada has been a democratic state for the last 4 elections with at least a 2% difference in favor of the democrats in the last two elections.

@@

North Carolina has been an exclusively Republican state since 1980, with a singular exception in 2008 when the state was democratic and voted for Obama. This means that North Carolina voted for Trump in th last two elections, in 2016 there was more significant win for the republican with 49.8% of the vote, with 46.2% going to the Democrats. While in 2020, the Republicans maintained their support from the state but the margin of victory was slimmer with them receiving 49.9% of the vote and Biden getting 48.8%.

@@

Harris is currently leading the polls in Michigan with 49% of the vote and Trump with 47%, this is a rather slim margin, but the first in the discussed states where Harris is leading in the polls. In @fig-supportAM we can see that there was a significant jump for Harris and a small dip in October followed by a gradual increase leading up to the elections. When we look at the voting history of the state in the last two elections, the have voted for the same candidates as Arizona and Georgia, where they voted for Biden in 2020 and for Trump in 2016, with the voting percentages at 50.6% to 47.8% in 2020 and 47.5% to 47.3 in 2016 with respect to the winner. Although unlike the previously mentioned states 2016 was the first time the state voted for the republican candidate since 1992. Considering Michigan is home to the largest black majority city in the United states, Detroit, and a large majority of union workers who often vote democratic as it is seen as the more union-friendly party between the two it is rather like that Harris will win the state.

@@

Second, Similarly to Nevada and Michigan Pennsylvania Voted for Trump in 2016 with a 48.2% to a 47.5% victory, and for Biden in 2020 with a slightly more significant but not overwhelming victory at 50% to 48.8%. 2016 was the first time Pennsylvania voted for a republican candidate since 1988.

@@

Lastly, if we look at Wisconsin's voting history, the only time Wisconsin voted Republican since 1988 was in 2016 when the state gave its electoral votes for Trump with 47.2% of the vote to Clinton's 46.5. then in 2020 the state went back to blue with Biden winning the state, allt hings considered out of all states we took into account Harris is likely to win.

@@

Without considering the swing states and if we assume all the other states will vote as expected Kamala Harris has a slight lead of 226 electoral votes to Donald Trump's 219. Now, if we take the 43 combined votes of Arizona, Georgia, and North Carolina, and add it to Trumps tally. While allocate Nevada, Michigan, Pennsylvania, and Wisconsin's votes to Harris which sum up to 50 electoral votes. This totals to a Democratic victory for Kamala Harris at 276 votes to Donald Trump's 262, we have come to the conclusion that Kamala Harris is likely to win the upcomming United States election by 14 electoral votes.

>>>>

Here we will discuss how we believe each state wwill vote both base on data we collected, the models we created and the voting history of each of these swing states in past elections.

@@

Arizona is a very important swing state especially as the state has switches which party they voted for in in the last two elections with Trump winning 49% of the vote and Clinton with 45.5%, which considering Arizona is a swing state is a rather significant6 margin. While in the 2020 election Biden ended up winning Arizona with 49.4% of the vote and Trump 49.1%, which is a much smaller margin of victory and what makes Arizona so questionable in the 2024 election. We can see in @fig-supportAM that while the polling numbers for Harris started somewhat low around 42%, the have gone up significantly and have continued to trend upwards in the most recent polls. Although, in the @fig-supportstate trump still has larger support in the state, and the largest polling difference in Trump's favour out of all the swing states polled @towin270.

@@

In @fig-supportGNN at the beginning of the polling data the support for Harris was relatively low, while it did start to grow the polling percentage somewhat plateaued at around 47.5% and does not show any signs of growing. Furthermore, in @fig-supportstate we can see that Trump has the edge over Harris considering all of these factors there is a very real possibility that Trump does win Georgia at the end of the day @towin270.

@@

Nevada is a state who's majority is dessert and wilderness, with two large cities being Reno and Las Vegas, as the case is with many states a Majority of democratic votes come from large cities and the majority of republican votes coming from rural areas. Nevada has been a democratic state for the last 4 elections with at least a 2% difference in favor of the democrats in the last two elections @towin270.

@@

North Carolina has been an exclusively Republican state since 1980, with a singular exception in 2008 when the state was democratic and voted for Obama. This means that North Carolina voted for Trump in th last two elections, in 2016 there was more significant win for the republican with 49.8% of the vote, with 46.2% going to the Democrats. While in 2020, the Republicans maintained their support from the state but the margin of victory was slimmer with them receiving 49.9% of the vote and Biden getting 48.8% @towin270.

@@

Harris is currently leading the polls in Michigan with 49% of the vote and Trump with 47%, this is a rather slim margin, but the first in the discussed states where Harris is leading in the polls. In @fig-supportAM we can see that there was a significant jump for Harris and a small dip in October followed by a gradual increase leading up to the elections. When we look at the voting history of the state in the last two elections, the have voted for the same candidates as Arizona and Georgia, where they voted for Biden in 2020 and for Trump in 2016, with the voting percentages at 50.6% to 47.8% in 2020 and 47.5% to 47.3 in 2016 with respect to the winner. Although unlike the previously mentioned states 2016 was the first time the state voted for the republican candidate since 1992. Considering Michigan is home to the largest black majority city in the United states, Detroit, and a large majority of union workers who often vote democratic as it is seen as the more union-friendly party between the two it is rather like that Harris will win the state @towin270.

@@

Second, Similarly to Nevada and Michigan Pennsylvania Voted for Trump in 2016 with a 48.2% to a 47.5% victory, and for Biden in 2020 with a slightly more significant but not overwhelming victory at 50% to 48.8%. 2016 was the first time Pennsylvania voted for a republican candidate since 1988 @towin270.

@@

Lastly, if we look at Wisconsin's voting history, the only time Wisconsin voted Republican since 1988 was in 2016 when the state gave its electoral votes for Trump with 47.2% of the vote to Clinton's 46.5% then in 2020 the state went back to blue with Biden winning the state, all things considered out of all states we took into account Harris is likely to win @towin270.

@@

Without considering the swing states and if we assume all the other states will vote as expected Kamala Harris has a slight lead of 226 electoral votes to Donald Trump's 219. Now, if we take the 43 combined votes of Arizona, Georgia, and North Carolina, and add it to Trumps tally. While allocate Nevada, Michigan, Pennsylvania, and Wisconsin's votes to Harris which sum up to 50 electoral votes. This totals to a Democratic victory for Kamala Harris at 276 votes to Donald Trump's 262, we have come to the conclusion that Kamala Harris is likely to win the upcomming United States election by 14 electoral votes. Below we have included an image of what we believee the electoral map will look after the election November 5th, @towin270:
